\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Coordimate\\Project Plan}
\date{December 2023}
\author{Ali Bassam, Vlada Prikhodchenko, Valentin Vikhorev}

\begin{document}

\maketitle

\section{Introduction}

\textit{In this section provide an introduction to the project. This can be similar to
a summary of the vision document. Provide the information needed to understand
the project. What problem are you trying to solve?}

\section{Description}

\subsection{Overview}

\textit{In this section provide an overview of the development plan. How will
development be conducted? What will be developed first? Are there any special
considerations that need to be accounted for before, during or after
development?}

\subsection{Organizational Diagrams}

\textit{Use this section to provide any diagrams or illustrations that accompany the
development plan.}

\subsection{Details}

\textit{This section, including following sections and subsections, will provide any
in depth detailing about the plan that are required in order to outline the
development procedure and process. What is the order in which the components
will be worked on and why?}

\section{Team}

\subsection{Members}

\textit{List the team members}

\subsection{Roles}

\textit{List each team members role to be performed during the development}
   
\subsection{Team Assignments}

\begin{center}
    \begin{tabular}
        { |c|c| }
        \hline
        Member name & Role \\
        \hline
        cell1 & cell2 \\
        cell4 & cell5 \\
        cell7 & cell8 \\
        \hline
    \end{tabular}
\end{center}

\section{Estimates and Deadline}

\textit{List here rough estimates for time and code. These should provide a course
outline for the required man power for the project.}

\end{document}

