\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Coordimate\\Design Document}
\date{December 2023}
\author{Ali Bassam, Vlada Prikhodchenko, Valentin Vikhorev}

\begin{document}

\maketitle

\section{Considerations}

\subsection{Assumptions}

\textit{In this section describe any assumptions, background, or dependencies of the
software, its use, the operational environment, or significant project issues.}

\subsection{Constraints}

\textit{In this section describe any constraints on the system that have a significant
impact on the design of the system.}

\subsection{System Environment}

\textit{In this section describe the system environment on which the software will be
executing. Include any specific reasons why this system was chosen and if there
are any plans to include new sections to the list of current ones.}


\section{Architecture}

\subsection{Overview}

\textit{Provide here a descriptive overview of the software/system/application
architecture.}

\subsection{Component Diagrams}

\textit{Provide here the diagram and a detailed description of its most valuable
parts. There may be multiple diagrams. Include a description for each diagram.
Subsections can be used to list components and their descriptions.}

\subsection{Class Diagrams}

\textit{Provide here any class diagrams needed to illustrate the application. These
can be ordered by which component they construct or contribute to. If there is
any ambiguity in the diagram or if any piece needs more description provide it
here as well in a subsection.}

\subsection{Sequence Diagrams}

\textit{Provide here any sequence diagrams. If possible list the use case they
contribute to or solve. Provide descriptions if possible.}

\subsection{Deployment Diagrams}

\textit{Provide here the deployment diagram for the system including any information
needed to describe it. Also, include any information needed to describe future
scaling of the system.}

\subsection{Other Diagrams}

\textit{Provide here any additional diagrams and their descriptions in subsections.}

\section{User Interface Design}

\textit{Provide here any user interface mock-ups or templates. Include explanations to
describe the screen flow or progression.}


\section{Appendices and References}

\subsection{Definitions and Abbreviations}

\textit{List here any definitions or abbreviations that could be used to help a new
team member understand any jargon that is frequently referenced in the design
document.}

\subsection{References}

\textit{List here any references that can be used to give extra information on a topic
found in the design document. These references can be referred to using
superscript in the rest of the document.}

\end{document}
